О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-09 pps-linear-bound/pps-linear-lower-bound.tex
Linguistic fix

In the present paper we improve Solymosi's results:
firstly, we obtain a greater constant $c$ in Theorem (TODO: the number of theorem and the exact constant),
using the combined approach with the Point Packing in a Square problem;
then, we prove that $l(m,n)=1$ for all $m$ and $n$ which it is correctly defined on.

>>>>

In the present paper we improve Solymosi's results:
firstly, we obtain a greater constant $c$ in Theorem (TODO: the number of theorem and the exact constant),
using the combined approach with the Point Packing in a Square problem;
then, we prove that $l(m,n)=1$ for all possible $m$ and $n$.
